XXX

### 2012-03-25 paper/engNERwiki.tex
Some fixes + deleted a paragraph.

Supervised Named Entity Recogizers require

@@

One approach to reduce the manual intervention required in language resource production, and thus ultimately production costs is automatically generating resources. An other approach to achieve this aim is using collaborative annotation and/or collaboratively constructed resources, such as Wikipedia, Wiktionary or Linked Open Data. Researchers apply the Web-as-corpus approach, often dealing with such datasets as Google's Web 1T 5-gram collection or DBpedia.

@@

Wikipedia is recognized as one of the largest available collection of entities, and also as an external knowledge to improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations (e.g.~Toral and Mu\~noz \shortcite{Toral:06}). Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al.~\shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

Wikipedia's knowledge may be incorporated as features in NER learning, e.g.~Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

To our knowledge, such type of automatically built corpora are not freely available, with the one exception of the Semantically Annotated Snapshot of the English Wikipedia \cite{Zaragoza:07}. It provides a wide range of linguistic information: POS tags, dependency labels, WordNet super senses and NE annotation according to WSJ and CoNLL tagsets. However, they followed a different way: the NEs were tagged by high quality open source softwares. Our corpora is available under the same license as Wikipedia's one (Creative Commons Attribution-Sharealike 3.0 Unported License).

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough 
%(XXX ez mit jelent?) elég nagy :)
corpora is given for less resourced languages, as well. Since our method is mainly XXX language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities XXX detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first automatically NE-annotated corpus for Hungarian.

@@

Beside regular articles, Wikipedia also contains redirect and disambiguation pages, which require special treatment. Redirect pages are empty, and are safe to ignore altogether. Disambiguation pages contain text, usually in the form of an enumeration of page links with a short description. Full sentences are scarce, and the structure of these pages makes it hard to extract valid training sentences from them. Therefore, disambiguation pages are dropped from the corpus as well.

@@

From the available NER annotation standards we elected to use the CoNLL \cite{Tjong:03} NE types. It is not difficult to see the parallels XXX between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the CoNLL NE categories PERSON, ORGANIZATION and LOCATION. The fourth category, MISCELLANEOUS is more elusive; according to the ConLL NER annotation guide\footnote{http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt}, the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other classes outside the main hierarchies.

While the correspondence described above holds for most classes in the XXX sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but according to the CoNLL annotation scheme, they are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, CoNLL does not recognize such entities.

To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class--NE category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign the category of the class that matches it most closely to the entity. If no match is found, the entity is tagged with \texttt{O}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main hierarchies, exceptions like those mentioned above, and the various classes that belong to the MISC category according to the CoNLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph (CITE). This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. There are two ways to tackle this problem. The first is to follow the DBpedia guidelines and only retain the first parent. The second method is manually deciding the right NE mapping for the ambiguous XXX class and adding it to the mapping file.

The first approach, unfortunately, already fails to assign the correct ConLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation, while ConLL's one refers it as a Location. Therefore, only the second, manual approach ensures correct tagging. XXX

%The full mapping can be found in Appendix~\ref{sec:appa}.

Using the mapping described above, we compile an entity list that contains all entities in DBpedia tagged with the appropriate CoNLL named entity category.

>>>>

@@

One approach to reduce the manual intervention required in language resource production, and thus ultimately production costs is automatically generating resources. Another approach to achieve this aim is using collaborative annotation and/or collaboratively constructed resources, such as Wikipedia, Wiktionary or Linked Open Data. Researchers apply the Web-as-corpus approach, often dealing with such datasets as Google's Web 1T 5-gram collection or DBpedia.

@@

Wikipedia is recognized as one of the largest available collection of entities, and also as a resource that can improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations (e.g.~Toral and Mu\~noz \shortcite{Toral:06}). Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al.~\shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

The knowledge in Wikipedia may be incorporated as features in NER learning, e.g.~Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

To our knowledge, such type of automatically built corpora are not freely available, with the one exception of the Semantically Annotated Snapshot of the English Wikipedia \cite{Zaragoza:07}. It provides a wide range of linguistic information: POS tags, dependency labels, WordNet super senses and NE annotation according to WSJ and CoNLL tagsets. However, they followed a different way: the NEs were tagged by high quality open source softwares. In contrast, our approach relies on the manual judgement of thousands of Wikipedia volunteers.

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough 
corpora is given for less resourced languages, as well. Since our method is largely language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first automatically NE-annotated corpus for Hungarian.

@@

@@

From the available NER annotation standards we elected to use the CoNLL \cite{Tjong:03} NE types. It is not difficult to see the parallels between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the CoNLL NE categories PERSON, ORGANIZATION and LOCATION. The fourth category, MISCELLANEOUS is more elusive; according to the ConLL NER annotation guide\footnote{http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt}, the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other classes outside the main hierarchies.

While the correspondence described above holds for most classes in the sub-hierarchies, there are some exceptions. For instance, the class \texttt{SportsLeague} is part of the \texttt{Organisation} sub-hierarchy, but according to the CoNLL annotation scheme, they are tagged as MISC. Similarly, the class \texttt{SportsTeamSeason} is under \texttt{Event}, by which account it would be classified as MISC; however, CoNLL does not recognize such entities.

To account for these misclassification, as well as the miscellaneous classes outside the main hierarchies, we have introduced a mapping mechanism. We created a file of DBpedia class--NE category mappings. Whenever an entity is evaluated, we look up its class, as well as the ancestors of its class, in the mapping, and assign to it the category of the class that matches it most closely. If no match is found, the entity is tagged with \texttt{O}. Since we take advantage of the inheritance hierarchy, the mapping list remains short: it contains only the root classes of the main hierarchies, exceptions like those mentioned above, and the various classes that belong to the MISC category according to the CoNLL annotation guideline.

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph\footnote{http://blog.dbpedia.org/2011/09/11/dbpedia-37-released-including-15-localized-editions}. This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \texttt{Library}, which can be traced back to both \texttt{Place} and \texttt{Organisation}.

DBpedia guidelines suggest that only the first parent is retained. Unfortunately, this approach already fails to assign the correct ConLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefer \texttt{Organisation}; ConLL's prefer LOCATION. Hence, we picked the right NE mapping manually and added it to the mapping file.

% The full mapping can be found in Appendix~\ref{sec:appa}.
%
Using the mapping described above, we compile an entity list that contains all entities in DBpedia tagged with the appropriate CoNLL named entity category.
